### 2020-05-01 README.Rmd
increased logo size
typos

<img src="inst/figures/logo.png" width = 120 alt="dataaimsr Logo"/>

@@

The API Key can be passed to each function as an additional `apiKey='XXXX'` argument, however it is preferred that API Keys are not stored in code.

@@

[A more detailed example of the R package usage on the weather dataset page.](10.25845/5c09bf93f315d/example-1.nb.html)  This is an [R Studio](https://www.rstudio.com/) Notebook and can be used interactively from *R Studio*.  __Note that you need to have an AIMS Data Platform API Key available to run this detailed example.__

>>>>

<img src="inst/figures/logo.png" width = 200 alt="dataaimsr Logo"/>

@@

The API Key can be passed to the package functions as an additional `api_key = 'XXXX'` argument, however it is preferred that API Keys are not stored in code.

@@

[A more detailed example of the R package usage on the weather dataset page.](10.25845/5c09bf93f315d/example-1.nb.html)  This is an [RStudio](https://www.rstudio.com/) Notebook and can be used interactively from [RStudio](https://www.rstudio.com/).  __Note that you need to have an AIMS Data Platform API Key available to run this detailed example.__
